Minimizing post-shock forecasting error using disparate information

### 2020-08-20 manuscript/manuscript.tex
minor edits to manuscript; we are almost done!

\maketitle
\begin{abstract}
    We develop a forecasting methodology for providing credible forecasts for time series that have recently undergone a shock. We achieve this by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock effect estimators are motivated with the aim of minimizing average forecast risk. We propose risk-reduction propositions that provide conditions that establish when our methodology works. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential prospective success of post-shock forecasts. Leave-one-out cross validation with $k$ random draws is proposed to estimate correctness of risk-reduction propositions, prospectively informing users of the probabilities that this prospective evaluation is in line with the reality. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure. Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical}. In our model, the donor pool can consist of dependent time series but time series within the donor pool should be independent of the time series of interest. However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method. 
%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point. 
We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. Our auto regressive model will consider present day covariates to better motivate similarity weighting. The considered adjustment strategies all target the mean of the shock effect distribution. Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop. We also motivate a simple leave-one-out cross validation with $k$ random draws procedure which can prospectively assess the performance of our shock effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020. We will show that our proposed adjustment estimators yield much better results than no adjustment in this setting. We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts. We now motivate our framework for post-shock forecasting.

@@

 \begin{enumerate}[label = (\roman*)]
    \item Under $\mc{M}_{1}$, $\E{\hat{\alpha}_{\rm adj}}=\E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha}$.
    \item Under $\mc{M}_{21}$, 
    \begin{align*}
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1} 
      \quad \text{ and } \quad 
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} .
    \end{align*}
    \item Under $\mc{M}_{22}$,
    \begin{align*}
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1}
      \quad \text{ and } \quad 
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} .
    \end{align*}
  \end{enumerate}
Formal justification for these results can be found in Appendix. Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$. Notice that under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$ (see distributional details of $\alpha_1$ in Section \ref{modelsetup}). Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$. Thus, we collect these results  as the following proposition.

@@

Section \ref{conditions} details conditions needed for risk-reduction and comparisons of adjustment estimators. These conditions involve variances and expectations which may be difficult to compute in practice. To make use of those conditions in practice, estimation is required. Sections \ref{varbootstrap} introduce parametric bootstrap, which estimates the involved parameters in those conditions and thus motivates prospective decision-making  about whether $\hat{\alpha}_i$ reduces the risk. Section
 \ref{loocv} describes  leave-one-out cross validation with $k$ random draws procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study. Our simulations verify these procedures.

@@

As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$. We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$. That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.  In fact, more generally, using similar proof of Lemma \ref{risklemma}, it can be shown that under $\mc{M}_2$, the risk-reduction quantities are
\begin{align*}
  \Delta(\hat{\alpha}_{\rm adj}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2,\\
  \Delta(\hat{\alpha}_{\rm IVW}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2 ,\\
  \Delta(\hat{\alpha}_{\rm wadj}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}},
\end{align*}
where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using the bootstrap and leave-one-out cross validation with $k$ random draws techniques developed in Sections \ref{varbootstrap} and \ref{loocv}.

@@

@@

Recall that $\mathbf{W}^*$  may not be unique if the conditions in Proposition \ref{uniqueness} are not satisfied. Non-uniqueness might be a concern theoretically. It is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$'s all targeting on the same $\alpha_1$. For example, consider the case where the size of  donor pool to be 2, $\var{\hat{\alpha}_2}=1$, $\var{\hat{\alpha}_3}=2$, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$. In this scenario, the weighted adjustment estimator induced by $\mathbf{W}^*_1$ has variance 1 whereas the one by $\mathbf{W}^*_2$ has variance 2. Nevertheless, even if $\hat{\alpha}_i$ has the same variance across $i = 2, \ldots, n+1$, the same issue would occur if there were infinitely many $\mbf{W}^*$ with different norms. It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}). However, non-uniqueness of $\mathbf{W}^*$ would not be a problem for inferential purposes. This is because all risk-reduction propositions and other properties established will still hold. Simulation examples listed in the Section 4 of the Supplementary Materials verify this point.

@@

@@

\begin{enumerate}
\item[(1)] {\bf Selection of model}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.  For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$. The model of $\alpha_i$ incorporates daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange (CBOE) volatility index. In contrast, the model of $y_{i,t}$ disregards CBOE volatility index. It is because CBOE volatity index is a metric for capturing market risk and  sentiment, which can be highly related to the shock effect that results from investor behavior.  It is not favorable in the model of $y_{i,t}$ since it may hinder  the estimation of $\alpha_i$.
\item[(3)] {\bf Construction of donor pool}. Our donor pool consists of Conoco Phillips shock effects observed in the past. We consider shock effects which occurred on March 14, 2008, several days in September, 2008, and November 27, 2014. The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession. In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}. These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Mac in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}. The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}. %The reasons for those three shocks are.
%  \begin{enumerate}
%  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities. On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank. The day of the announcement, the stocks of other major Wall Street firms tumbled (including Conoco Phillips). These concerns then spilled over into the broader universe of stocks \citep{shorter2008bear}. %In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
%  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets. The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}. Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
%  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}. During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}. 
%  \end{enumerate}
\end{enumerate}

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well, and they do not recover the magnitude of the shock effect but are much better than unadjusted forecasts that do not account for shock effects. 
The unadjusted forecast misses the post-shock response by 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively. 
%Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. Moreover, the risk-reduction quantities are consistent with the reality as well. 
The true shock effect is not fully recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$. This may be a result of a poorly constructed donor pool. The shock on March 9th, 2020 is in the midst of the COVID-19 pandemic and oil production volatility. It is difficult to find available stock market time series data that were generated under a similar setting. In any event, the shock on March 9th, 2020 was the largest price shock to Conoco Phillips shares by a wide margin, even after adjusting for inflation.

@@

There have been several other recent  methods developed for forecasting COVID-19 cases. For example, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be appropriate for post-shock forecasting but may be too dependent upon model specification for the shock distribution. \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. \citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool. Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.

@@

We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock. Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast. We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings. The model, under which we verify these claims, is a simple AR(1) model. Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models. %for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.

Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent. As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock. But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock effects in the donor pool. 
%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 6$.
%This generalization was adopted in Section \ref{forecasting}. In this case, the variance expressions proposed in Section \ref{properties} will not work. However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock effects (not necessarily mutually independent) in the donor pool are independent of the one of interest. 
Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its first and second moments exist. The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.  We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts. An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis. Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.

>>>>

\maketitle
\begin{abstract}
    We develop a forecasting methodology for providing credible forecasts for time series that have recently undergone a shock. We achieve this by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcomes are observed. Three shock effect estimators are motivated with the aim of minimizing average forecast risk. We propose risk-reduction propositions that provide conditions that establish when our methodology works. Bootstrap and leave-one-out cross validation procedures are provided to prospectively assess the performance of our methodology. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

In this article, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random-effect structure. Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical}. In our model, the donor pool can consist of dependent time series but time series within the donor pool should be independent of the time series of interest. However, mutual independence among time series in the donor pool can aid prospective evaluation of the reliability of our method. 
%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point. 
We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. Our auto regressive model will consider present day covariates to better motivate similarity weighting. The considered adjustment strategies all target the mean of the shock effect distribution. Such an estimation strategy can reduce mean squared error (MSE) when variation in the shock effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions can be estimated by a residual bootstrap procedure that we develop. We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock effect adjustment estimators. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction propositions are nearly perfectly correct when the model for the shock effects is identified well with appropriate covariates under a fixed design. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020. We will show that our proposed adjustment estimators yield much better results than no adjustment in this setting. We also use this example to demonstrate settings in which the shock effect may be decomposed into separate estimable parts. We now motivate our framework for post-shock forecasting.

@@

 \begin{enumerate}[label = (\roman*)]
    \item Under $\mc{M}_{1}$, $\E{\hat{\alpha}_{\rm adj}}=\E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha}$.
    \item Under $\mc{M}_{21}$, 
    $
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \delta' \mbf{x}_{i, T_i^*+1}
    $
    and
    $
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \delta'\mbf{x}_{1, T_1^*+1} .
    $
    \item Under $\mc{M}_{22}$,
    $
      \E{\hat{\alpha}_{\rm adj}} = \mu_{\alpha} + \frac{1}{n} \sum_{i=2}^{n+1} \mu_{\delta}' \mbf{x}_{i, T_i^*+1}
    $
    and
    $
       \E{\hat{\alpha}_{\rm wadj}} = \mu_{\alpha} + \mu_{\delta}'\mbf{x}_{1, T_1^*+1} .
    $
  \end{enumerate}
Formal justification for these results can be found in Appendix. Note that $\hat{\alpha}_{\rm adj}$, $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$ are not unbiased estimators for $\alpha_1$. However, under $\mc{M}_{1}$, $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm adj}$ are unbiased estimators for $\E{\alpha_1}=\mu_{\alpha}$. Nevertheless, $\hat{\alpha}_{\rm adj}$ is a biased estimator for $\E{\alpha_1}$ but $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator for $\E{\alpha_1}$ under both $\mc{M}_{21}$ and $\mc{M}_{22}$. We collect these results in the following proposition.

@@

Section \ref{conditions} details conditions needed for risk-reduction and comparisons of adjustment estimators. These conditions involve variances and expectations which may be difficult to compute in practice. To make use of those conditions in practice, estimation is required. Sections \ref{varbootstrap} introduce parametric bootstrap, which estimates the involved parameters in those conditions and thus motivates prospective decision-making  about whether $\hat{\alpha}_i$ reduces the risk. Section
 \ref{loocv} describes our leave-one-out cross validation procedures, which prospectively estimate the correctness of such decision without observation of the post-shock response for the time series under study. Our simulations verify these procedures.

@@

As mentioned in Section \ref{constructionofestimators}, it is difficult to evaluate the expectation and variance of $\hat{\alpha}_{\rm IVW}$. We note that $\hat{\alpha}_{\rm IVW}$ is generally biased for $\E{\alpha_1}$. That is to say we can adapt the above proof to derive the risk-reduction conditions for $\hat{\alpha}_{\rm IVW}$: under $\mc{M}_{1}$, $\mc{M}_{21}$, and $\mc{M}_{22}$, $\Delta(\hat\alpha_{\rm IVW}) > 0$ when $\var{\hat{\alpha}_{\rm IVW}} +(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2<(\E{\alpha_1})^2$.  In fact, more generally, using similar proof of Lemma \ref{risklemma}, it can be shown that under $\mc{M}_2$, the risk-reduction quantities are
\begin{align*}
  \Delta(\hat{\alpha}_{\rm adj}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}}-(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2,\\
  \Delta(\hat{\alpha}_{\rm IVW}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}}-(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2 ,\\
  \Delta(\hat{\alpha}_{\rm wadj}) 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}},
\end{align*}
where we estimate $\Delta(\hat{\alpha})$ for estimator $\hat\alpha$  using bootstrap and leave-one-out cross validation procedures developed in Sections \ref{varbootstrap} and \ref{loocv}.

@@

There are some philosophical distinctions between $\mc{B}_u$ and $\mc{B}_f$. $\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors. In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error. A double bootstrap procedure with similar steps can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$. The double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, can check whether a bootstrap percentile interval of resampled estimates of $\Delta(\hat{\alpha})$ contain 0 at a desired error threshold. We investigated such a double bootstrap procedure and found that it produced inferences that were similar to those produced using the bootstrap techniques developed in the main text.

@@

Recall that $\mathbf{W}^*$  may not be unique if the conditions in Proposition \ref{uniqueness} are not satisfied. Non-uniqueness might be a concern theoretically. This is due to the fact that infinitely many different weights can lead to infinitely many non-unique $\hat{\alpha}_{\rm wadj}$'s all targeting on the same $\alpha_1$. For example, consider the case where the size of  donor pool to be 2, $\var{\hat{\alpha}_2}=1$, $\var{\hat{\alpha}_3}=2$, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$. In this scenario, the weighted adjustment estimator induced by $\mathbf{W}^*_1$ has variance 1 whereas the one by $\mathbf{W}^*_2$ has variance 2. Nevertheless, even if $\hat{\alpha}_i$ has the same variance across $i = 2, \ldots, n+1$, the same issue would occur if there were infinitely many $\mbf{W}^*$ with different norms. It is possible to resolve this issue by selecting a unique weight $\mbf{W}^*$ that optimizes a desirable objective function, prior to which one should find the bases spanning the subspace of $\mbf{W}^*$ satisfying (\ref{SCM}). Simulations in the Section 4 of the Supplementary Materials provide some evidence that non-uniqueness of $\mathbf{W}^*$ is not problematic for inferences.

@@

We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population in these simulations.  Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$. In this scenario, $\mathbf{W}^*$ will take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.  When $p < n$ and there exists some $\mathbf{W}^*\in \mc{W}$ satisfies (\ref{SCM}), $\mc{B}_u$ fails since the non-uniqueness due to $p < n$ will guarantee degeneracy of  $\mathbf{W}^*$. However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$. Moreover, simulations in Section 4 of the Supplementary Materials show that non-uniqueness does not seriously compromise the inference.

@@

\begin{enumerate}
\item[(1)] {\bf Selection of model}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}.  For these reasons, we will consider 30 pre-shock trading days and we will forecast the immediate shock effect. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We consider different covariates for the model of $\alpha_i$ and $y_{i, t}$. The model of $\alpha_i$ incorporates daily S\&P 500 index prices, West Texas Intermediate (WTI) crude oil prices, dollar index, 13 Week treasury bill rates, and Chicago Board Options Exchange volatility index (VIX). The model for $y_{i,t}$ disregards VIX. This is because VIX is a metric for capturing market risk and sentiment, which is highly influential for the shock effect model.
\item[(3)] {\bf Construction of donor pool}. Our donor pool consists of Conoco Phillips shock effects observed in the past. We consider shock effects which occurred on March 14, 2008, several days in September, 2008, and November 27, 2014. The first sets of shock effects were observed during recessions that possessed similar characteristics to the current recession. In particular, all of these recessions were predicated by an inversion of the yield curve \citep{bauer2018economic}. These 2008 shock effects correspond to the collapse of Bear Stearns, the placement of Fannie May and Freddie Mac in conservatorship on September 7th, the collapse of Lehman Brothers on September 15th, and the closing of Washington Mutual on September 25th \citep{shorter2008bear, ewing2013volatility, dwyer2009financial, longstaff2010subprime}. The last shock effect corresponds to an OPEC induced supply side shock effect \citep{huppmann2015opec}. %The reasons for those three shocks are.
%  \begin{enumerate}
%  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities. On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank. The day of the announcement, the stocks of other major Wall Street firms tumbled (including Conoco Phillips). These concerns then spilled over into the broader universe of stocks \citep{shorter2008bear}. %In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
%  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets. The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}. Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
%  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}. During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}. 
%  \end{enumerate}
\end{enumerate}

@@

We can see from Figure~\ref{Fig:CP} that $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$ and $\hat{\alpha}_{\text{IVW}}$ perform decently well. Our estimation framework misses the yet to be observed pot-shock response, however they perform much better than unadjusted forecasts that do not account for shock effects. The unadjusted forecast misses the post-shock response by 9.870 dollars whereas 
the use of $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ misses by $5.324$, $5.392$, and $5.813$ dollars, respectively. 
%Therefore, the risk-reduction propositions are consistent with the reality  with the reduced risks for forecasts using  $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$ than without. Moreover, the risk-reduction quantities are consistent with the reality as well. 
The true shock effect is not fully recovered by $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$. This may be a result of a poorly constructed donor pool. The shock on March 9th, 2020 is in the midst of the COVID-19 pandemic and oil production volatility. It is difficult to find available stock market time series data that were generated under a similar setting. In any event, the shock on March 9th, 2020 was the largest price shock to Conoco Phillips shares by a wide margin, even after adjusting for inflation.

@@

@@

We developed a methodology for forecasting post-shock response values after the occurrence of a structural shock. Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock effect estimator to the original forecast. There have been several other recent similar methods developed for forecasting COVID-19 cases. For example, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be appropriate for post-shock forecasting but may be too dependent upon model specification for the shock distribution. \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. \citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provided useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool. Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.

We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock effect settings. The model, under which we verify these claims, is a simple AR(1) model. Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models. Generally, multiple shock effects can be nested within a time series; and time series in the donor pool can be dependent. As an example, we  considered a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock. But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock effects in the donor pool. 
%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \tilde{\varepsilon}_i$ for $i = 6$.
%This generalization was adopted in Section \ref{forecasting}. In this case, the variance expressions proposed in Section \ref{properties} will not work. However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock effects (not necessarily mutually independent) in the donor pool are independent of the one of interest. 
Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that its first and second moments exist. The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$.  We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts. An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis. Although our work is developed for time-series or AR$(p)$ models, in fact, it can be generalized to any similar setting with a model of the response, whose parameters can be estimated unbiasedly, an additive shock-effect structure, and the structure that the time series in the donor pool are independent of the one of interest.
